%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% LuaLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
%Template amended by: Wren Warren, 2024
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\makeatletter
\renewcommand*{\@biblabel}[1]{\hfill#1.}
\makeatother

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

\renewcommand\refname{Bibliography}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Wren Warren -- Curriculum Vit\ae} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 240 Kelton St Apt. 2,\\ % Address line 1
\> Allston MA, 02134 \\ % Address line 2
%{\bf Date of Birth} \> April 9$^{th}$, 1994 \\ % Date of birth 

\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> (207) 607-1518 \\ % Mobile phone
{\bf E-mail} \> \href{mailto:warrenandros@gmail.com}{warrenandros@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

I am a data scientist with significant experience in medical and especially neurological data, who desires to reshape the way we analyze medical data by using machine learning techniques to develop better holistic models of neurological disease onset and recovery. I enjoy problem-solving and exploring alternative and innovative techniques for analyzing, modeling, and predicting data. I also believe strongly in ethical and socially-conscious use of artificial intelligence and machine learning, recognizing that biased programmers may create biased algorithms that portray a majority-dominant perspective without adequate input from marginalized communities.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2021-2024} \> Masters of Science - \href{https://graduate.northeastern.edu/program/master-of-science-in-data-science-boston-5256/}{Northeastern University, Massachusetts} \\[5pt]
\>\ Data Science \\
\>\+ \textit{Current}
}

%------------------------------------------------

\tabbedblock{
\bf{2018-2020} \> Non-Degree - \href{https://extension.harvard.edu}{Harvard University, Massacusetts}\\[5pt]
\>\ Pre-Med Post-Baccalaureate Program, Extension School \\
}

%------------------------------------------------

\tabbedblock{
\bf{2017-2018} \> Non-Degree - \href{https://cps.northeastern.edu}{Northeastern University, Massacusetts}\\[5pt]
\>\ Pre-Med Post-Baccalaureate Program, College of Professional Studies \\
}

%------------------------------------------------

\tabbedblock{
\bf{2012-2016} \> Bachelors of Science - \href{https://www.tufts.edu}{Tufts University, Massacusetts}\\[5pt]
\>\ Major in Coginitive and Brain Science \\
\>\ Minor in Computer Science \\
\>\ Tufts Varsity Crew, 2012 - 2016
}

%----------------------------------------------------------------------------------------
%	RESEARCH SECTION
%----------------------------------------------------------------------------------------

\section{Research Experience}

I have experienced many different aspects of the research process, including designing and running psychology experiments, analyzing data, and running and analyzing research MRIs, managing complicated datasets and databases, and performing statistical analyses, as well as writing and editing submissions to the IRB for multiple research projects.

\job
{7/2021 -}{Present}
{\textbf{J. Philip Kistler Stroke Research Center}, Massachusetts General Hospital, 175 Cambridge Street Suite 300, Boston, MA, United States}
{https://www.massgeneral.org/neurology/stop-stroke/research/j-philip-kistler-stroke-research-center}
{Clinical Data Manager}
{
\begin{itemize}
\item All duties and knowledge of previous role
\item Managing all aspects of intensive data projects such as the upgrading of databases to new structures, completely reorganizing databases to be more stable and more helpful to researchers
\item Training and managing coordinators on projects involving the processing and transmission of data
\item Developing new systems and operating procedures for the center to further ensure proper data handling by all researchers.
\item Independently managing IRB protocols and coordinating data use agreements for many Primary Investigators.
\item Creating extensive documentation, converting old databases to future-forward formats, training successor.
\end{itemize}
\rule{0mm}{5mm}\textbf{Technologies:} Microsoft SQL Server, syngo MR XA30, syngo MR VE11C, Microsoft Access, Python, REDCap, Microsoft Excel, Bash Scripting, Total Commander, Synedra, Analyze 11.0}

%------------------------------------------------

\job
{7/2017 -}{7/2021}
{\textbf{J. Philip Kistler Stroke Research Center}, Massachusetts General Hospital, 175 Cambridge Street Suite 300, Boston, MA, United States}
{https://www.massgeneral.org/neurology/stop-stroke/research/j-philip-kistler-stroke-research-center}
{Neuroimaging Clinical Research and Data Coordinator II}
{
\begin{itemize}
\item Building on previous role, in addition managing multiple databases, handling all data queries requested from the research center by multiple PIs, labs, and sites.
\item Assisting in the formatting and analysis of neurovascular data for numerous research projects resulting in published papers.
\item Personal handling of in-house data metrics, financial statistic reporting, feasibility surveys, IRB amendments and Data Use Agreements.
\item Maintaining and building databases, training other database users and data managers on the data structure, the special circumstances of multiple databases, general good data maintenance practices and specific variable nuances and definitions.
\item Training and managing coordinators on reading CTs for hemorrhagic outcome markers, and coordinating the download and codification of clinical CTs and MRIs.
\item Performing research MRIs on research subjects in 1.5T, 3T and 7T environments, with visual stimuli, hypercapnia tasks, and blood pressure reduction tasks.
\end{itemize}
\rule{0mm}{5mm}\textbf{Technologies:} syngo MR VE11C, Microsoft Access, Python, REDCap, Microsoft Excel, Bash Scripting, Total Commander, Synedra, Analyze 11.0}

%------------------------------------------------

\job
{7/2016 -}{7/2017}
{\textbf{J. Philip Kistler Stroke Research Center}, Massachusetts General Hospital, 175 Cambridge Street Suite 300, Boston, MA, United States}
{https://www.massgeneral.org/neurology/stop-stroke/research/j-philip-kistler-stroke-research-center}
{Neuroimaging Clinical Research Coordinator I}
{
\begin{itemize}
\item Trained to read Computed Tomography and Magnetic Resonance imaging for intracerebral hemorrhage and acute ischemic stroke measurements and risk factors, including hemorrhage volume, white matter disease scoring, brain atrophy scale, infarct presence, microhemorrhage presence, and location of stroke.
\item Completed 1600-subject case analysis of subject data and imaging measurements for a hemorrhagic stroke cohort
\end{itemize}
\rule{0mm}{5mm}\textbf{Technologies:} syngo MR VE11C, Microsoft Access, REDCap, Microsoft Excel, Synedra, Analyze 11.0, Epic Hyperspace}

%------------------------------------------------

\job
{2/2015 -}{5/2016}
{\textbf{Memory and Cognition Laboratory}, Tufts University, 490 Boston Avenue, Somerville, MA, United States}
{https://as.tufts.edu/psychology/research/labs}
{Research Assistant}
{
Senior Poster on Memory and Cognition of Assorted Word Groups \\
\rule{0mm}{5mm}\textbf{Technologies:} SPSS, QuickBasic}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\job
{7/2021 -}{Present}
{\textbf{J. Philip Kistler Stroke Research Center}, Massachusetts General Hospital, 175 Cambridge Street Suite 300, Boston, MA, United States}
{https://www.massgeneral.org/neurology/stop-stroke/research/j-philip-kistler-stroke-research-center}
{Clinical Data Manager}
{
\begin{itemize}
\item Creation of a conclusive Data Management Guidelines document detailing all aspects related to data operations of my position.
\item Migrating a series of databases into SQL back-end formats to stabilize data and allow for more security.
\item Reorganization of a samples database from multiple possible IDs for one subject down to one ID per subject in a specific table, in order to prevent the possibility of a sample being doubled, including a full analysis of sample matching.
\end{itemize}
}

%------------------------------------------------

\job
{7/2021 -}{Present}
{\textbf{J. Philip Kistler Stroke Research Center}, Massachusetts General Hospital, 175 Cambridge Street Suite 300, Boston, MA, United States}
{https://www.massgeneral.org/neurology/stop-stroke/research/j-philip-kistler-stroke-research-center}
{Clinical Data Manager}
{
\begin{itemize}
\item Creation of a conclusive Data Management Guidelines document detailing all aspects related to data operations of my position.
\item Migrating a series of databases into SQL back-end formats to stabilize data and allow for more security.
\item Reorganization of a samples database from multiple possible IDs for one subject down to one ID per subject in a specific table, in order to prevent the possibility of a sample being doubled, including a full analysis of sample matching.
\end{itemize}
}

%------------------------------------------------

\job
{7/2016 -}{7/2021}
{\textbf{J. Philip Kistler Stroke Research Center}, Massachusetts General Hospital, 175 Cambridge Street Suite 300, Boston, MA, United States}
{https://www.massgeneral.org/neurology/stop-stroke/research/j-philip-kistler-stroke-research-center}
{Clinical Research Coordinator}
{
\begin{itemize}
\item Maintaining a database of MRI and CT scans of patients with hemorrhagic stroke
\item Searching for, retrieving, and performing the file conversions of MRI and CTs to prepare the scans for advanced analyses
\item Performing quantitative analysis of CT/MRI scans obtained from patients enrolled in our hospital based as well as multicenter studies
\item Storing the 3D lesion maps, recording the volumetric analysis results in our database
\item Maintaining and writing scan processing scripts
\item Reviewing CT scan analysis with interns
\item Assisting in processing of imaging data from multi-center studies 
\item Updating and maintaining SOPs, guidelines and data forms for MGH and multi-center studies 
\item Assisting with informed consent of patients eligible for neuroimaging based clinical trials
\item Assisting with drafting project and grant applications
\item Searching medical literature and retrieving journal articles and other references
\item Maintaining and overseeing regulatory documentation for MGH and multi-center studies 
\item Taking call approximately one weekend per month and 5 weeknights per month to help cover off hour study enrollments and procedures
\item Coordinating and/or performing study procedures including but not limited to interviews, sample processing, phlebotomy and other protocol-specific clinical skills
\item Assisting with other research-related administrative tasks as needed
\item Maintaining IRB files and communication with IRB for specific studies
\item Coordinating clinical research data collection, analysis, reporting and organization 
\item Developing programs to check the integrity of the data, including range, error, and logic checks
\item Assisting staff with system-related questions or problems.
\item Collaborating with study investigators and research fellows on the design of data queries to retrieve data and generate reports for projects and abstracts
\item Developing simple user interfaces for data entry, workflow management and querying
\item Assisting with designing and running regular reports on the quantity of data and quality in the data management system.
\item Ensuring accuracy and completeness of data files and subject research files and provide support documents detailing file organization 
\item Assisting study coordinators and project/program managers with data-related amendments to the IRB including development and execution of Data Use Agreements
\item Providing technical and research assistance to staff members with regard to both general technology and database-specific questions and troubleshooting
\end{itemize}
}

%------------------------------------------------

\job
{2011 -}{2013}
{\textbf{University of Maine 4-H Camp and Learning Center at Tanglewood}, 1 Tanglewood Road, Lincolnville, ME, United States}
{https://extension.umaine.edu/tanglewood/tanglewood-lincolnville/}
{Day Camp Educator}
{
\begin{itemize}
\item Structured and facilitated learning of children aged 4 – 8 in a hands-on, natural environment.
\item Guided children to learn to solve problems as a group and on their own, including group challenges, investigations into natural phenomena, and artistic projects.
\item Worked as a senior member of the learning team to devise strategies to promote learning and fun in nature.
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer Software Skills}

\skillgroup{Programming Languages}
{
\textit{C++, Python, HTML, CSS, QuickBasic, Microsoft VBA, SQL, R, SAS, LaTeX}\\
}

%------------------------------------------------

\skillgroup{Applications}
{
\textit{Microsoft Office, Analyze 11.0, Synedra, Epic Hyperspace, Total Commander, DICOM Query/Retrieve Server, SPSS}\\
}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY SECTION
%----------------------------------------------------------------------------------------

\begin{thebibliography}{99}

\raggedright

\bibitem{Abramson} Abramson JR, Castello JP, Keins S, Kourkoulis C, Rodriguez-Torres A, Myserlis EP, Alabsi H, \textbf{Warren AD}, Henry JQA, Gurol ME, Viswanathan A, Greenberg SM, Towfighi A, Skolarus L, Anderson CD, Rosand J, Biffi A. Biological and Social Determinants of Hypertension Severity Before vs After Intracerebral Hemorrhage. Neurology. 2022 Mar 29;98(13):e1349-e1360. doi: 10.1212/WNL.0000000000200003

\bibitem{Biffi} Biffi A, Teo KC, Castello JP, Abramson JR, Leung IYH, Leung WCY, Wang Y, Kourkoulis C, Myserlis EP, \textbf{Warren AD}, Henry J, Chan KH, Cheung RTF, Ho SL, Anderson CD, Gurol ME, Viswanathan A, Greenberg SM, Lau KK, Rosand J. Impact of Uncontrolled Hypertension at 3 Months After Intracerebral Hemorrhage. J Am Heart Assoc. 2021 Jun;10(11):e020392. doi: 10.1161/JAHA.120.020392

\bibitem{Castello} Castello JP, Teo KC, Abramson JR, Keins S, Takahashi CE, Leung IYH, Leung WCY, Wang Y, Kourkoulis C,
Pavlos Myserlis E, \textbf{Warren AD}, Henry J, Chan KH, Cheung RTF, Ho SL, Gurol ME, Viswanathan A, Greenberg
SM, Anderson CD, Lau KK, Rosand J, Biffi A. Long-Term Blood Pressure Variability and Major Adverse
Cardiovascular and Cerebrovascular Events After Intracerebral Hemorrhage. J Am Heart Assoc. 2022 Mar
15;11(6):e024158. doi: 10.1161/JAHA.121.024158

\bibitem{Das} Das AS, Gokcal E, Regenhardt RW, \textbf{Warren A}, Schwab K, Viswanathan A, Greenberg SM, Rost NS, Rosand J Schwamm LH, Gurol ME. Atrial Fibrillation is Associated With Severe Basal Ganglia Perivascular Spaces [WP238]. Stroke 2020; 51(Suppl\_1): AWP238

\bibitem{De Kort} De Kort AM, Kuiperij HB, Marques TM, Jäkel L, van den Berg E, Kersten I, van Berckel-Smit HEP, Duering M, Stoops E, Abdo WF, Rasing I, Voigt S, Koemans EA, Kaushik K, \textbf{Warren AD}, Greenberg SM, Brinkmalm G, Terwindt GM, Wermer MJH, Schreuder FHBM., Klijn CJM, Verbeek MM. Decreased Cerebrospinal Fluid Amyloid β 38, 40, 42, and 43 Levels in Sporadic and Hereditary Cerebral Amyloid Angiopathy. Ann Neurol. 2023;93: 1173-1186. https://doi.org/10.1002/ana.26610

\bibitem{Dowlatshahi} Dowlatshahi D, Morotti A, Al-Ajlan FS, Boulouis G, \textbf{Warren AD}, Petrcich W, Aviv RI, Demchuk AM, Goldstein JN. Interrater and Intrarater Measurement Reliability of Noncontrast Computed Tomography Predictors of Intracerebral Hemorrhage Expansion. Stroke. 2019;50(5):1260-1262. doi:10.1161/STROKEAHA.118.024050

\bibitem{Fotiadis 1} Fotiadis P, van Veluw S, Salat D, \textbf{Warren A}, Grill S, Schwab K, Zollei L, Viswanathan A, Gurol ME, Greenberg SM. Loss of Gray-White Contrast in Cerebral Amyloid Angiopathy: An in-vivo and Ex-Vivo Exploratory Approach [TMP109]. Stroke 2019; 50(Suppl\_1): ATMP109

\bibitem{Fotiadis 2} Fotiadis P, Pasi M, Charidimou A, \textbf{Warren AD}, Schwab KM; Alzheimer’s Disease Neuroimaging Initiative, Rosand J, van der Grond J, van Buchem MA, Viswanathan A, Gurol ME, Greenberg SM. Decreased Basal Ganglia Volume in Cerebral Amyloid Angiopathy. J Stroke. 2021 May;23(2):223-233. doi: 10.5853/jos.2020.04280

\bibitem{Freeze} Freeze WM, Zanon Zotin MC, Scherlek AA, Perosa V, Auger CA, \textbf{Warren AD}, van der Weerd L, Schoemaker D, Horn MJ, Gurol ME, Gokcal E, Bacskai BJ, Viswanathan A, Greenberg SM, Reijmer YD, van Veluw SJ. Corpus callosum lesions are associated with worse cognitive performance in cerebral amyloid angiopathy. Brain Commun. 2022 Apr 26;4(3):fcac105. doi: 10.1093/braincomms/fcac105

\bibitem{Gokcal} Gokcal E, Horn MJ, van Veluw SJ, Frau-Pascual A, Das AS, Pasi M, Fotiadis P, \textbf{Warren AD}, Schwab K, Rosand J, Viswanathan A, Polimeni JR, Greenberg SM, Gurol ME. Lacunes, Microinfarcts, and Vascular Dysfunction in Cerebral Amyloid Angiopathy. Neurology. 2021 Mar 23;96(12):e1646-e1654. doi: 10.1212/WNL.0000000000011631

\bibitem{Horn} Horn MJ, Gokcal E, Becker AJ, Das AS, \textbf{Warren AD}; Alzheimer Disease Neuroimaging Initiative, Schwab K, Goldstein JN, Biffi A, Rosand J, Polimeni JR, Viswanathan A, Greenberg SM, Gurol ME. Cerebellar atrophy and its implications on gait in cerebral amyloid angiopathy. J Neurol Neurosurg Psychiatry. 2022 May 9:jnnp-2021-328553. doi: 10.1136/jnnp-2021-328553

\bibitem{Li 1} Li Q, \textbf{Warren AD}, Qureshi AI, Morotti A, Falcone GJ, Sheth KN, Shoamanesh A, Dowlatshahi D, Viswanathan A. Ultra-Early Blood Pressure Reduction Attenuates Hematoma Growth and Improves Outcome in Intracerebral Hemorrhage. Ann Neurol. 2020. doi:10.1002/ana.2579

\bibitem{Li 2} Li Q, Zotin MC, \textbf{Warren AD}, Ma Y, Gurol ME, Goldstein JN, Greenberg SM, Charidimou A, Raposo N, Viswanathan, A. CT-visible convexity subarachnoid hemorrhage is associated with cortical superficial siderosis and predicts recurrent ICH. Neurology. 2020; doi:10.1212/wnl.0000000000011052

\bibitem{Morotti 1} Morotti A, Boulouis G, Charidimou A, Li Q, Poli L, Costa P, De Giuli V, Leuci E, Mazzacane F, Busto G, Arba F, Brancaleoni L, Giacomozzi S, Simonetti L, Laudisi M, Micieli G, Cavallini A, Candeloro E, Gamba M, Magoni M, \textbf{Warren AD}, Anderson CD, Gurol ME, Biffi A, Viswanathan A, Casetta I, Fainardi E, Zini A, Pezzini A, Padovani A, Greenberg SM, Rosand J, Goldstein JN. Hematoma Expansion in Intracerebral Hemorrhage With Unclear Onset. Neurology. 2021 May 11;96(19):e2363-e2371. doi: 10.1212/WNL.0000000000011895

\bibitem{Morotti 2} Morotti A, Boulouis G, Charidimou A, Poli L, Costa P, Giuli V, Leuci E, Mazzacane F, Busto G, Arba F, Brancaleoni L, Giacomozzi S, Simonetti L, Laudisi M, Cavallini A, Gamba M, Magoni M, Cornali C, Fontanella MM, \textbf{Warren AD}, Gurol EM, Viswanathan A, Gasparotti R, Casetta I, Fainardi E, Zini A, Pezzini A, Padovani A, Greenberg SM, Rosand J, Goldstein JN. Imaging markers of intracerebral hemorrhage expansion in patients with unclear symptom onset. Int J Stroke. 2022 Jan 4:17474930211068662. doi: 10.1177/17474930211068662

\bibitem{Morotti 3} Morotti A, Boulouis G, Nawabi J, Charidimou A, Pasi M,Schlunk F, Shoamanesh A, Katsanos A, Mazzacane F, Busto G, Arba F, Brancaleoni L, Giacomozzi S, Simonetti L, \textbf{Warren AD}, Laudisi M, Cavallini A, Gurol ME, Viswanathan A, Zini A, Casetta I, Fainardi E, Greenberg SM, Padovani A, Rosand J, and Goldstein JN. Association between hematoma expansion severity and outcome and its interaction with baseline intracerebral hemorrhage volume. Neurology. 2023;101(16). doi:10.1212/wnl.0000000000207728

\bibitem{Morotti 4} Morotti A, Boulouis G, Nawabi J, Li Q, Charidimou A, Pasi M, Schlunk F, Shoamanesh A, Katsanos AH, Mazzacane F, Busto G, Arba F, Brancaleoni L, Giacomozzi S, Simonetti L, \textbf{Warren AD}, Laudisi M, Cavallini A, Gurol ME, Viswanathan A, Zini A, Casetta I, Fainardi E, Greenberg SM, Padovani A, Rosand J, Goldstein JN. Using noncontrast computed tomography to improve prediction of intracerebral hemorrhage expansion. Stroke. 2023;54(2):567-574. doi:10.1161/strokeaha.122.041302

\bibitem{Pasi} Pasi M, Pongpitakmetha T, Charidimou A, Singh SD, Tsai H, Xiong L, Boulouis G, \textbf{Warren AD}, Rosand J, Frosch MP, Viswanathan A, Gurol ME, Greenberg SM. Cerebellar Microbleed Distribution Patterns and Cerebral Amyloid Angiopathy. Stroke. 2019;50(7):1727-1733. doi:10.1161/STROKEAHA.119.024843

\bibitem{Thanakit} Pongpitakmetha T, Fotiadis P, Pasi M, Boulouis G, Xiong L, \textbf{Warren AD}, Schwab KM, Rosand J, Gurol ME, Greenberg SM, Viswanathan A, Charidimou A. Cortical superficial siderosis progression in cerebral amyloid angiopathy: Prospective MRI study. Neurology. 2020;94(17):e1853-e1865. doi:10.1212/WNL.0000000000009321

\bibitem{Sanjula} Singh SD, Pasi M, Schreuder FHBM, Morotti A, Senff JR, \textbf{Warren AD}, McKaig BN, Schwab K, Gurol ME, Rosand J, Greenberg SM, Viswanathan A, Klijn CJM, Rinkel GJE, Goldstein JN, Brouwers HB. Computed Tomography Angiography Spot Sign, Hematoma Expansion, and Functional Outcome in Spontaneous Cerebellar Intracerebral Hemorrhage. Stroke. 2021 Aug;52(9):2902-2909. doi: 10.1161/STROKEAHA.120.033297

\bibitem{Su} Su CM, \textbf{Warren A}, Kraus C, Macias-Konstantopoulos W, Zachrison KS, Viswanathan A, Anderson C, Gurol ME, Greenberg SM, Goldstein JN. Lack of racial and ethnic-based differences in acute care delivery in intracerebral hemorrhage. Int J Emerg Med. 2021 Jan 19;14(1):6. doi: 10.1186/s12245-021-00329-w

\bibitem{Teo} Teo KC, Keins S, Abramson JR, Leung WCY, Leung IYH, Wong Y, Yeung C, Kourkoulis C, \textbf{Warren AD}, Chan K, Cheung RTF, Ho S, Gurol ME, Viswanathan A, Greenberg SM, Anderson CD, Lau K, Rosand J, Biffi A. Blood pressure control targets and risk of cardiovascular and cerebrovascular events after intracerebral hemorrhage. Stroke. 2023;54(1):78-86. doi:10.1161/strokeaha.122.039709

\bibitem{van den Berg} van den Berg E, de Kort AM, Kersten I, Brinkmalm G, Johansson K, Marques T, Jäkel L, Gobom J, Stoops E, Portelius E, Gkanatsiou E, Abdo WF, Rasing I,Voigt S, Koemans EA, Kaushik K, \textbf{Warren AD}, Greenberg SM, Terwindt GM, Wermer MJH, Klijn CJM, FHBM, Zetterberg H, Blennow K, Kuiperij HB, M. Verbeek MM. Profiling amyloid‐β peptides as diagnostic biomarkers for cerebral amyloid angiopathy. Alzheimers Dement. 2023;19(S15). doi:10.1002/alz.076080

\bibitem{Warren} \textbf{Warren AD}, Li Q, Schwab K, Greenberg SM, Viswanathan A, Rosand J, Gurol ME, Patel AB, Goldstein JN. External ventricular drain placement is associated with lower mortality after intracerebral hemorrhage with intraventricular hemorrhage. Int J Emerg Med. 2022;15(1). doi:10.1186/s12245-022-00450-4

\bibitem{Wilker} Wilker EH, Mostofsky E, Fossa A, Koutrakis P, \textbf{Warren A}, Charidimou A, Mittleman MA, Viswanathan A. Ambient Pollutants and Spontaneous Intracerebral Hemorrhage in Greater Boston. Stroke. 2018 Oct 18:2764-2766. doi: 10.1161/STROKEAHA.118.023128. PMID: 30580707

\bibitem{Yogendrakumar} Yogendrakumar V, Ramsay T, Fergusson D, Demchuk AM, Aviv RI, Rodriguez-Luna D, Molina CA, Silva Y, Dzialowski I, Kobayashi A, Boulanger J, Lum C, Gubitz G, Srivastava P, Roy J, Kase CS, Bhatia R, Hill MF, \textbf{Warren AD}, Anderson CD, Gurol ME, Greenberg SM, Viswanathan A, Rosand J, Goldstein JN, Dowlatshahi D. New and expanding ventricular hemorrhage predicts poor outcome in acute intracerebral hemorrhage. Neurology. 2019;93(9):e879-e888. doi:10.1212/WNL.0000000000008007


\end{thebibliography}

%----------------------------------------------------------------------------------------
%	REFERENCE SECTION
%----------------------------------------------------------------------------------------

\section{References}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Zora DiPucchio \\ % Reference name
{\bf Company} \> J. Philip Kistler Stroke Research Center \\ % Reference company
{\bf Position} \> Sr. Program Manager \\ % Reference job title 
{\bf E-mail} \> \href{mailto:ZDIPUCCHIO@mgh.harvard.edu}{ZDIPUCCHIO@mgh.harvard.edu} \\ % Reference contact information
{\bf Phone} \> (617) 726-7710 % Reference contact information


\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Joshua N. Goldstein\\ % Reference name
{\bf Company} \> Massachusetts General Hospital \\ % Reference company
{\bf Position} \> Co-Director, Center for Neurologic Emergencies, Department of Emergency Medicine \\ % Reference job title 
{\bf E-mail} \> \href{mailto:JGOLDSTEIN@mgh.harvard.edu}{JGOLDSTEIN@mgh.harvard.edu} % Reference contact information
{\bf Phone} \> (617) 724-3290 % Reference contact information
\end{tabbing}}

%----------------------------------------------------------------------------------------

\end{document}